# Tasks

* have B-dependent variables output by p-BC rather than pre-determined
    - update this for plotters
* generalize: input series directly into function
    - actually for sims don't do this unless you put the loop outside the function
* get rid of t() where possible

---

# The great transposition of 2024

```{r}
# --- symmetry checking function
sym <- function(x){
  return(x == t(x))
}
```

| Variable  | Original Dim      | New Dim           | Details                       |
|:----------|:------------------|:------------------|:------------------------------|
| v         | N x K             | K x N             | Size N slepians, prelims      |
| vb        | B x K             | K x B             | Size B slepians, function     |
| (st)      | N x length(freqs) | length(freqs) x N | Matrix of signals             |
| mat       | B x B             | B x B             | Funky kernel **SYMMETRIC!**   |
| mvec      | B x B             | B x B             | eigenvecs of mat (NOT SYM)    |
| a (func)  | out = 1 x NF      | NFx 1?            | expansion coef output         |
|           | in = 20*NF x N-B+1| rev?              | input: SWHRS                  |



```{r}
z <- matrix(sw2[,1], nrow = NF)
```


```{r}
oingo  <- (K/(mval[1]*w0.0)) * t(sapply(b, function(p){mvec[,1] %*% matrix(sw [,p], ncol = NF)}))
boingo <- (K/(mval[1]*w0.0)) * t(sapply(b, function(p){matrix(sw2[,p], nrow = NF) %*% mvec[,1]}))

bingo  <- (K/(mval[1]*w0.0)) * sapply(b, function(p){mvec[,1] %*% matrix(sw [,p], ncol = NF)})
bongo  <- (K/(mval[1]*w0.0)) * sapply(b, function(p){matrix(sw2[,p], nrow = NF) %*% mvec[,1]})

    # Initialize arrays
    bc1 <- array(dim = c(NF,N,M))

bc1[,tb,1] <- bongo 

    # Endpoints: 1st derivative
    tds.start  <- tds(sw2,1)
    tds.end    <- tds(sw2,max(b)) 

    # Extrapolate
      bc1[,1:(tb[1]-1),m]   <- sapply((tb[1]-1):1, 
                                        function(h){ bc1[,tb[1],m] - h*tds.start })
      bc1[,(max(tb)+1):N,m] <- sapply(1:(B2-(B2 != B/2)), 
                                        function(h){ bc1[,max(tb),m] + h*tds.end })



z  <- sapply((tb[1]-1):1, function(h){ bc1[,tb[1],m] - h*tds.start })
zz <- sapply(1:(B2-(B2 != B/2)), function(h){ bc1[,max(tb),m] + h*tds.end })

image.plot(bc1[,1:(tb[1]-1),1])
plot(colSums(bc1[,,1]))
```

---

```{r}
oingo <- matrix(1:4,ncol=1)
boingo <- crossprod(1:4)

t(oingo) %*% oingo
oingo %*% t(oingo)

 crossprod(oingo,oingo)
tcrossprod(oingo,oingo)
```

---

plots that worked

```{r}
image.plot(pbc$bc1$mean, main = "new")
image.plot(pbc$bc2$mean, main = "new")
image.plot(info$tru$xtf + info$tru$xtf2, main = "tru")
image.plot(info$tru$xtf, main = "tru")
type == GUMP
type = "GUMP"
yf.true  <- if(type != "noise"){AR2.spec(ar2)  } else {NULL}
yf2.true  <- if(type == "GUMP"){AR2.spec(ar2.2)} else {NULL}
xtf.true  <- if(type == "AR2"    ){ ytf.true
} else if(type == "UMP"    ){ outer(ct^2,  yf.true)
} else if(type == "GUMP"   ){ outer(ct1^2, yf.true) + outer(ct2^2, yf2.true)
} else if(type == "AR2_non"){
1e2/(Mod(1 - (a.12)%*%exp(-i*2*pi*Fs) - psi.2%*%exp(-i*2*pi*Fs*2))^2)
}
image.plot(xtf.true)
xtf.true  <- if(type == "AR2"    ){ ytf.true
} else if(type == "UMP"    ){ outer(ct^2,  yf.true)
} else if(type == "GUMP"   ){ outer(yf.true, ct1^2) + outer(yf2.true, ct2^2)
} else if(type == "AR2_non"){
1e2/(Mod(1 - (a.12)%*%exp(-i*2*pi*Fs) - psi.2%*%exp(-i*2*pi*Fs*2))^2)
}
image.plot(xtf.true)
image.plot(pbc$bc1$mean, main = "new")
```


```{r}
par(bg = "red4")

my.cols <- 400:409

jj <- tcrossprod(coef(SOBI(pbc$bc1$mean[,my.cols])),pbc$bc1$mean[,my.cols])

kk <- ts(t(jj))
plot(kk, main = paste(min(my.cols),":", max(my.cols)))
```

```{r}
# animation::
```

